### 2015-11-14 paper/paper.tex
fixed cookie issue with volksrant.nl, but it persists with telegraafnl (we may want to skip oveir the site). Spider should now work for the volkskrant.

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\title{Illustrating Text}
\author{Christopher Catton, Partick Murphy, Charles Ung}
\begin{document}
\section{Abstract}
\section{Generating Dataset(s)}
In our study we created our own dataset(s) in order to generate a dataset containing the data we need. We generated the dataset by crawling and scraping separate news sites. Our data is tuple of the source, date, and text of an article.
Instead of gathering data related to images, we use google image search to generate a set of images related to a set and subsets of the words we extract from a text. In other related studies this task can be done by adding images that appear with a text, but we chose to use google image search to reduce the amount of scraping we need to do to generate our dataset.
\end{document}

### 2015-11-14 datacollecter/datacollecter/items.py

@@ -15,7 +15,9 @@ class DatacollecterItem(scrapy.Item):
 
 class ArticleItem(scrapy.Item):
     title = scrapy.Field()
+    time = scrapy.Field()
     text = scrapy.Field()
+    url = scrapy.Field()
     images = scrapy.Field()
 
 class ImageItem(scrapy.Item):

### 2015-11-14 datacollecter/datacollecter/settings.py

@@ -30,7 +30,7 @@ NEWSPIDER_MODULE = 'datacollecter.spiders'
 #CONCURRENT_REQUESTS_PER_IP=16
 
 # Disable cookies (enabled by default)
-#COOKIES_ENABLED=False
+COOKIES_ENABLED=True
 
 # Disable Telnet Console (enabled by default)
 #TELNETCONSOLE_ENABLED=False

### 2015-11-14 datacollecter/datacollecter/spiders/telegraafnl.py

@@ -1,0 +1,51 @@
+import scrapy
+
+from datacollecter.items import ArticleItem
+
+class telegraafSpider(scrapy.Spider):
+    name = "telegraaf"
+    allowed_domains = ["telegraaf.nl", "tmgonlinemedia.nl"]
+    start_urls = ["http://www.telegraaf.nl"]
+
+    count = 0
+    max_count = 100000
+
+    def parse(self, response):
+        articles_onpage = response.xpath('.//@href')
+        #if self.is_article(response):
+        #yield self.parse_article(response)
+
+        #yield scrapy.Request(response.url, callback=self.parse_article)
+
+        item = ArticleItem()
+        article = response.xpath('//div[re:test(@id, "artikel")]') #including images, but not ads (preferably)
+        time = article.xpath('.//div[re:test(@class, "artDatePostings")]/span[re:test(@class, "datum")]/text()').extract()
+        title = article.xpath('.//h1/text()').extract()
+        intro = article.xpath('.//p[re:test(@class, "article__intro")]/text()').extract()
+        body = article.xpath('.//div[re:test(@id, "artikelKolom")]//p/text()').extract()
+        all_text = article.xpath('.//text()').extract()
+        if len(title) >= 1 and len(intro) >= 1 and len(all_text) >= 1:
+            item['title'] = title
+            item['time'] = time
+            item['text'] = ''.join(intro) + ''.join(body) #all_text
+            item['url'] = response.url
+            self.count = self.count + 1
+            print self.count
+            print item
+            yield item
+
+        if self.count < self.max_count:
+            for article in articles_onpage:
+                url = article.extract()
+                print url
+                for ad in self.allowed_domains:
+                    if url.startswith(ad) or url.startswith("http://www." + ad):
+                        yield scrapy.Request(url, callback=self.parse)
+                    elif url.startswith("/cookiewall/accept?"):
+                        yield scrapy.Request(self.start_urls[0] + url, callback=self.parse)
+                    elif url.startswith("/"):
+                        urln = "http://" + ad + url
+                        yield scrapy.Request(urln, callback=self.parse)
+        else:
+            print "MAX ARTICLE COUNT EXCEEDED"
+

### 2015-11-14 datacollecter/datacollecter/spiders/volkskrantnl.py

@@ -1,19 +1,70 @@
 import scrapy
-from crawler.items import ArticleItem
+#from scrapy.contrib.spiders import CrawlSpider, Rule
+#from scrapy.contrib.linkextractors.sgml import SgmlLinkExtractor
+from datacollecter.items import ArticleItem
 
-class volkskrantnlSpider:
+class volkskrantnlSpider(scrapy.Spider):
     name = "volkskrant"
     allowed_domains = ["volkskrant.nl"]
     start_urls = ["http://www.volkskrant.nl"]
+    count = 0
+    max_count = 100000
 
     def parse(self, response):
-        """find articles"""
-        articles_onpage = response.xpath('.//[re:test(@class, "ankeiler")//@href')
-        for article in articles_onpage:
-            url = article
-            yield scrapy.Request(url, callback=self.parse_article)
+        articles_onpage = response.xpath('.//@href')
+        #if self.is_article(response):
+        #yield self.parse_article(response)
+
+        #yield scrapy.Request(response.url, callback=self.parse_article)
+        print response.url
+        item = ArticleItem()
+        article = response.xpath('//article[re:test(@class, "article article--full")]') #including images, but not ads (preferably)
+        time = article.xpath('.//time[re:test(@class, "article__meta-time")]/text()').extract()
+        title = article.xpath('.//h1[re:test(@class, "article__title")]/text()').extract()
+        intro = article.xpath('.//p[re:test(@class, "article__intro")]/text()').extract()
+        #body = article.xpath('.//p[re:test(@class, "article__body__paragraph")]/text()').extract()
+        all_text = article.xpath('.//text()').extract()
+        if len(title) >= 1 and len(intro) >= 1 and len(all_text) >= 1:
+            item['title'] = title
+            item['time'] = time
+            item['text'] = all_text
+            item['url'] = response.url
+            self.count = self.count + 1
+            print self.count
+            yield item
+
+        if self.count < self.max_count:
+            for article in articles_onpage:
+                url = article.extract()
+                for ad in self.allowed_domains:
+                    if url.startswith(ad) or url.startswith("http://www." + ad):
+                        yield scrapy.Request(url, callback=self.parse)
+                    elif url.startswith("/cookiewall/accept?"):
+                        yield scrapy.Request(self.start_urls[0] + url, callback=self.parse)
+                    elif url.startswith("/"):
+                        urln = "http://" + ad + url
+                        yield scrapy.Request(urln, callback=self.parse)
+        else:
[…]

### 2015-12-06 image_subsets/comparators/avg_pixel_comparator.py
Added class that will calculate average colour within square regions of pixels in two images to see if they have a similiar average. Better than pixel by pixel comparison. However, it is limited to the fact that pixels have to be represented by the same number of bits(ie 8-bit and 24-bit versions of the same image will return False)

@@ -1,0 +1,87 @@
+#!/bin/python
+# -*- coding: utf-8 -*-
+
+import math
+import sys
+
+from PIL import Image
+
+class AvgPixelsComparator(object):
+    # Want to be able to tighten or loosen the comparison constraints 
+    def __init__(self, num_kernels_horizontal=2, num_kernels_vertical=2, avg_comparator=lambda x, y: x == y):
+        # This is an approximate number of kernels
+        self.__num_kernels_horizontal = num_kernels_horizontal
+        self.__num_kernels_vertical = num_kernels_vertical
+        self.__avg_comparator = avg_comparator
+
+    def compare(self, image1, image2):
+        # Algorithm won't work if any dimension doesn't satisfy the following conditions num_pixels < num_kernels + 2
+        if image1.width < self.__num_kernels_horizontal + 2 or image2.width < self.__num_kernels_horizontal + 2:
+            raise ValueError("Error: The heights of the provided images ({image1width}, {image2width}) are not greater than or equal to the requested number of kernels ({num_kernels} + 2)".format(image1width=image1.width, image2width=image2.width, num_kernels=self.__num_kernels_horizontal))
+            
+        if image1.height < self.__num_kernels_vertical + 2 or image2.height < self.__num_kernels_vertical + 2:
+            raise ValueError("Error: The heights of the provided images ({image1height}, {image2height}) are not greater than or equal to the requested number of kernels ({num_kernels} + 2)".format(image1height=image1.height, image2height=image2.height, num_kernels=self.__num_kernels_vertical))
+    
+        image1_kernel_width = self.__calc_dimension(image1.width, self.__num_kernels_horizontal)
+        image1_kernel_height = self.__calc_dimension(image1.height, self.__num_kernels_vertical)
+        image1_kernel_horizontal_move_amt = self.__calc_move_amount(image1.width, self.__num_kernels_horizontal)
+        image1_kernel_vertical_move_amt = self.__calc_move_amount(image1.height, self.__num_kernels_vertical)
+        
+        image2_kernel_width = self.__calc_dimension(image2.width, self.__num_kernels_horizontal)
+        image2_kernel_height = self.__calc_dimension(image2.height, self.__num_kernels_vertical)
+        image2_kernel_horizontal_move_amt = self.__calc_move_amount(image2.width, self.__num_kernels_horizontal)
+        image2_kernel_vertical_move_amt = self.__calc_move_amount(image2.height, self.__num_kernels_vertical)
+        
[…]

### 2015-12-06 image_subsets/image_subsets.py

@@ -85,6 +85,7 @@ This will produce 3 sets
 '''
 if __name__=="__main__":
     if len(sys.argv) == 2:
+        image_iterator.max_images_per_block = 1
         try:
             image_subsets = None
             with open(sys.argv[1], 'r') as subset_file:

### 2015-12-08 paper/paper.tex
Added section on generating relevant image set to the paper, and added a section which inludes talks about the problem caused by Google limiting the number of image searches we can do per day

@@
 We generated the dataset by crawling and scraping separate news sites.
+These new sites include the British Broadcasting Corporation, the New York Times, De Telegraaf, and De Volkskrant.
 Our data is tuple of the source, date, and text of an article.
@@
 In other related studies this task can be done by adding images that appear with a text, but we chose to use google image search to reduce the amount of scraping we need to do to generate our dataset.
+\section{Generating Relevant Image Set}
+After downloading images from the Google search image API of salient word sets from the article, the common subset of images within these sets must be found.
+This can be done by finding the intersection of all the sets.
+In our implemnetation, we first created subset that was the intersection of two sets and then iteratively performed the intersection of this subset with each other set of images.
+Since the number of images is relatively large, all the images in two sets could not be loaded into memory at once.
+To deal with this issue, the intersection algorithm used was a block-based intersection which loads two blocks of 50 images into memory, then compares each image in 1 block to each image in the other block and output images which are in both blocks.
+To compare the images two different comparison tests were used.
+For two images to be considered the same, they must pass either or both of the comparison tests.
+The first test was a simple pixel by pixel comparison, if for each pixel in each image the values of the pixels were equal then the two images are the same.
+The second comparison test was to take the average colour of all the pixels in a different square regions of the images and compare them.
+If the average colours in each of the regions were the same, then the images are considered the same.
+\section{Problems}
+One problem we encountered was that the Google image seach API only allows for 100 searches per day for free, so gathering enough images for each of the salient sets was impossible.
 \end{document}

### 2015-12-08 image_subsets/comparators/avg_pixel_comparator.py
Added README instructions for finding the common subsets of images

@@ -44,6 +44,7 @@ class AvgPixelsComparator(object):
                 
                 image1_y += image1_kernel_vertical_move_amt
                 image2_y += image2_kernel_vertical_move_amt
+                print kernel_avg_image1, kernel_avg_image2
                 if not self.__avg_comparator(kernel_avg_image1, kernel_avg_image2):
                     same_image = False
                     break
@@ -63,8 +64,10 @@ class AvgPixelsComparator(object):
         
     def __get_colour_avg_of_kernel(self, kernel_x, kernel_y, kernel_width, kernel_height, image):
         pixel_sum = 0
+        print "New Kernel"
         for i in range(kernel_width):
             for j in range(kernel_height):
+                print kernel_x, kernel_y, i, j, image.getpixel((int(kernel_x) + i, int(kernel_y) + j))
                 pixel_sum += image.getpixel((int(kernel_x) + i, int(kernel_y) + j))
         return pixel_sum / float(kernel_width * kernel_height)
             

### 2015-12-08 collage/collage.py
Added collage maker

@@ -1,0 +1,77 @@
+#!/usr/bin/env python
+
+import glob
+import math
+import os
+import sys
+from optparse import OptionParser
+
+from PIL import Image, ImageFont, ImageDraw
+
+import settings
+
+def debug(s):
+    sys.stderr.write('%s\n' % s)
+
+
+
+def makeCollage( listFiles = [], *args):
+
+
+    # List of input files.
+    infiles = listFiles
+    debug('Found %s input files.' % len(infiles))
+	
+    print infiles
+	
+    # Create canvas.
+    tile_count = len(infiles) + settings.TILE_OFFSET
+    COLS = settings.COLS
+    ROWS = tile_count // COLS + (1 if tile_count % COLS else 0)
+    imgsize = (2 * settings.PADDING + settings.TILE_SIZE[0] * COLS +
+               settings.GAP * (COLS - 1),
+               2 * settings.PADDING + settings.TILE_SIZE[1] * ROWS +
+               settings.GAP * (ROWS - 1))
+    img = Image.new('RGB', imgsize, settings.BGCOLOR)
+    debug('Creating a grid with %s columns and %s rows.' % (COLS, ROWS))
+
+	
+    imgno = 0
+    for tile_file in infiles:
+        debug('Processing %s...' % tile_file)
+
+        # Tile position.
+        pos = imgno + settings.TILE_OFFSET
+        x = pos % COLS
+        y = pos // COLS
+        # Offsets.
+        xoff = settings.PADDING + x * (settings.TILE_SIZE[0] + settings.GAP)
+        yoff = settings.PADDING + y * (settings.TILE_SIZE[1] + settings.GAP)
+
+        tile = Image.open(tile_file)
+
+        # Resize image if necessary
+        if settings.RESIZE and tile.size != settings.TILE_SIZE:
+            w_from, h_from = tile.size
+            if (w_from / float(h_from) >
+                settings.TILE_SIZE[0] / float(settings.TILE_SIZE[1])):
+                w_to = settings.TILE_SIZE[0]
+                h_to = int(w_to / float(w_from) * h_from)
+            else:
+                h_to = settings.TILE_SIZE[1]
+                w_to = int(h_to / float(h_from) * w_from)
+            tile = tile.resize((w_to, h_to), Image.ANTIALIAS)
+
+        # Place tile on canvas.
+        img.paste(tile, (xoff, yoff))
+		
+
+        imgno += 1
+
+    # Post-process image.
[…]

### 2015-12-08 collage/settings.py

@@ -1,0 +1,34 @@
+import os
+
+
+# Size of every image tile.
+#To decrease white space vertically lower the Y value of TILE_SIZE
+TILE_SIZE = 160, 175
+RESIZE = True  # Resize files that don't match the above?
+
+# Column width of image grid. Rows will be determined automatically.
+COLS = 6
+
+# Tile offset.
+# 0 will start at the top right, 1 will leave one empty tile, etc.
+TILE_OFFSET = 0
+
+# Outside padding (in px)
+PADDING = 5
+
+# Gap size between images (in px)
+GAP = 2
+
+# Background color
+BGCOLOR = '#fff'
+
+# Output dir
+subdir = lambda *d: os.path.join(os.path.dirname(__file__), *d)
+
+
+#change out put directory and file name of collage here
+OUTPUT_FILE = subdir('output', 'fullcollage1.jpg')
+
+
+# Post-processing of image. Default: Do nothing.
+post_process = lambda img: None

### 2015-12-09 textAnalysis/article.py
added code for dealing with multiple word sets

@@ -13,9 +13,12 @@ class ArticleDB(object):
         if isinstance(index, list):
             return None
         elif index >= 0:
-            return self.__collection.find(ref)[index]
+            return self.__collection.find()[index]
         elif index == -1:
             return self.__collection.find(ref)
+
+    def count(self):
+        return self.__collection.count()
     """
     def get(self, ref):
         if isinstance(ref, list):
@@ -73,6 +76,9 @@ class Article(object):
         w.superwords[word.lower()] = w.superwords.get(word.lower(), 0) + 1
 
     def __update_word__(self, word):
+        if word == ' ':
+            return
+        print word
         if self.words.get(word.lower(), None) == None:
             self.words[word.lower()] = Word(word)
 
@@ -91,28 +97,38 @@ class Article(object):
 
                     self.__update_subword__(sub_word, word)
 
-    def analyze(self):
+    def analyze(self, mxSetSize=1):
         words = self.text.replace('\n',' ')
         words = words.replace('\t',' ')
-        words = words.replace('.', ' ')
-        words = words.replace(',', ' ')
-        words = words.replace('/', ' ')
-        words = words.replace('(', ' ')
-        words = words.replace(')', ' ')
-        words = words.replace(';', ' ')
-        words = words.replace('\"', ' ')
-        words = words.replace('?', ' ')
-        words = words.replace('!', ' ')
-        words = words.replace('[', ' ')
-        words = words.replace(']', ' ')
+        words = words.replace('.', '')
+        words = words.replace(',', '')
+        words = words.replace('/', '')
+        words = words.replace('(', '')
+        words = words.replace(')', '')
+        words = words.replace(';', '')
+        words = words.replace('\"', '')
+        words = words.replace('?', '')
+        words = words.replace('!', '')
+        words = words.replace('[', '')
+        words = words.replace(']', '')
         words = words.split(' ')
         #rehersal_loop = []*self.__rehersal_loop_length__
+        wset = []
         for w in words:
-
             """
             get distance from previous words
             """
-            self.__update_word__(w)
+            if len(wset) >= mxSetSize:
+                temp = []
+                temp[0:(mxSetSize-1)] = wset[1:mxSetSize]
+                wset = temp
+            else:
+                wset.append(w)
+
+            for j in range(0, len(wset)+1):
+                #print wset[0:j]
+                #nw = ' '.join(wset[0:j])
+                self.__update_word__(' '.join(wset[0:j]))
 
[…]

### 2015-12-09 textAnalysis/generate_salient_sets.py

@@ -1,5 +1,15 @@
+def salient_sets(article_set, model):
+    print "Generating Salience Sets..."
+
+    print "Finished Generating Salience Sets..."
+    return []
+
+
 lang = LanguageModel_Mongo("", "dutch", None)
 articles = ArticleDB()
+
+a = articles.get(0)
+s = a.getSalientSets()
 
 #for each article
 #get words

### 2015-12-09 textAnalysis/generate_word_list.py

@@ -2,36 +2,33 @@ from pymongo import MongoClient
 from article import Article, ArticleDB
 from language import LanguageModel, LanguageModel_Mongo
 max_articles = 10
-
+mxSetSize = 1
+lang = "English"
 #def generate():
-client = MongoClient()
-db = client['text_illustrator']
-articles = db['articles'].find()
-#print articles
-dutch = LanguageModel("Dutch")
-dutch_mongo = LanguageModel_Mongo("", "dutch", None)
-parsed = 0
-#connect to db
-#for each article
 
-articleDB = ArticleDB()
-max_articles = 10 #articles.count()
-while (parsed < max_articles or max_articles == -1):
-    #print "Parsing Article"
-    a = articleDB.get(parsed)
-    txt = ' '.join(a['text'])
-    adate = ' '.join(a['time'])
-    url = ''.join(a['url'])
-    atitle = ' '.join(a['title'])
-    a = Article(text=txt, title=atitle, src=url, date=adate, nid=a['_id'], language_model=dutch)
-    a.analyze()
-    parsed += 1
+sites = ["bbc.com", "bbc.co.uk"]
+def generate_model(lang, sites, settings, mxParse=100):
+    model = LanguageModel(lang)
+    mongo = LanguageModel_Mongo("", lang, None)
+    parsed = 0
 
-#l = dutch.getWordsByFrequency()
-print "Inserting into Database"
-dutch_mongo.collection.drop()
-for k, w in dutch.words.iteritems():
-    dutch_mongo.__process_word__(w)
+    articleDB = ArticleDB()
+    while (parsed < mxParse or (max_articles == -1 and articleDB.count())):
+        a = articleDB.get(index=parsed)
+        txt = ' '.join(a.get('text',''))
+        adate = ' '.join(a.get('time',''))
+        url = ''.join(a.get('url',''))
+        atitle = ' '.join(a.get('title',''))
+        for s in sites:
+            if s in url:
+                a = Article(text=txt, title=atitle, src=url, date=adate, nid=a['_id'], language_model=model)
 
-print "Articles Parsed: ", articles.count()
-#generate()
+        a.analyze(mxSetSize)
+        parsed += 1
+
+    print "Parsed ", parsed, " Articles. Inserting into Database"
+    mongo.collection.drop()
+    for k, w in model.words.iteritems():
+        mongo.__process_word__(w)
+
+generate_model(lang, sites, None, 100)

### 2015-12-09 textAnalysis/article.py
- Saliency now works correctly. - Calculates frequency for word sets and keeps track of word set size - Add Language Info to keep track of language wide statistics

@@ -1,5 +1,6 @@
 from word import Word
 import pymongo
+from language import LanguageModel_Mongo, LanguageInfoModel_Mongo
 
 class ArticleDB(object):
     __client = pymongo.MongoClient()
@@ -75,16 +76,17 @@ class Article(object):
 
         w.superwords[word.lower()] = w.superwords.get(word.lower(), 0) + 1
 
-    def __update_word__(self, word):
+    def __update_word__(self, word, word_count):
         if word == ' ':
             return
-        print word
+        #print word
         if self.words.get(word.lower(), None) == None:
             self.words[word.lower()] = Word(word)
 
         if self.words[word.lower()].freq == 0:
             self.words[word.lower()].freq += self.words[word.lower()].sub_freq
         self.words[word.lower()].freq += 1
+        self.words[word.lower()].word_count = word_count
         """
         update frequency
         """
@@ -97,40 +99,11 @@ class Article(object):
 
                     self.__update_subword__(sub_word, word)
 
-    def analyze(self, mxSetSize=1):
-        words = self.text.replace('\n',' ')
-        words = words.replace('\t',' ')
-        words = words.replace('.', '')
-        words = words.replace(',', '')
-        words = words.replace('/', '')
-        words = words.replace('(', '')
-        words = words.replace(')', '')
-        words = words.replace(';', '')
-        words = words.replace('\"', '')
-        words = words.replace('?', '')
-        words = words.replace('!', '')
-        words = words.replace('[', '')
-        words = words.replace(']', '')
-        words = words.split(' ')
-        #rehersal_loop = []*self.__rehersal_loop_length__
-        wset = []
-        for w in words:
-            """
-            get distance from previous words
-            """
-            if len(wset) >= mxSetSize:
-                temp = []
-                temp[0:(mxSetSize-1)] = wset[1:mxSetSize]
-                wset = temp
-            else:
-                wset.append(w)
+    def analyze(self, mxSetSize=1, update_model=True):
+        for w in self.genWordSets(mxSetSize):
+            self.__update_word__(w[0], w[1])
 
-            for j in range(0, len(wset)+1):
-                #print wset[0:j]
-                #nw = ' '.join(wset[0:j])
-                self.__update_word__(' '.join(wset[0:j]))
-
-        if self.language_model != None:
+        if self.language_model != None and update_model:
             for k, v in self.words.iteritems():
                 #v.addArticle(self)
[…]

### 2015-12-09 textAnalysis/generate_salient_sets.py

@@ -1,15 +1,38 @@
+from pymongo import MongoClient
+from article import Article, ArticleDB
+from language import LanguageModel, LanguageModel_Mongo
+
+mxSetSize=1
+lang = "English"
+def get_article(article):
+    txt = ' '.join(a.get('text',''))
+    adate = ' '.join(a.get('time',''))
+    url = ''.join(a.get('url',''))
+    atitle = ""
+    if isinstance(a.get('title', []), list):
+        atitle = ' '.join(a.get('title',''))
+    elif isinstance(a.get('title', ""), basestring):
+        atitle = a.get('title', "")
+
+    return Article(text=txt, title=atitle, src=url, date=adate, nid=a['_id'], language_model=model)
+
 def salient_sets(article_set, model):
     print "Generating Salience Sets..."
-
+    ret = []
+    for a in article_set:
+        article = get_article(a)
+        article.analyze(mxSetSize, update_model=False)
+        ret.append(article.getSalientSets(model.lang))
     print "Finished Generating Salience Sets..."
-    return []
+    return ret
 
 
-lang = LanguageModel_Mongo("", "dutch", None)
+model = LanguageModel_Mongo("", lang, None)
 articles = ArticleDB()
 
 a = articles.get(0)
-s = a.getSalientSets()
+
+ret = salient_sets([a], model)
 
 #for each article
 #get words

### 2015-12-09 textAnalysis/generate_word_list.py

@@ -1,13 +1,13 @@
 from pymongo import MongoClient
 from article import Article, ArticleDB
-from language import LanguageModel, LanguageModel_Mongo
+from language import LanguageModel, LanguageModel_Mongo, LanguageInfoModel_Mongo
 max_articles = 10
-mxSetSize = 1
+mxSetSize = 3
 lang = "English"
 #def generate():
 
 sites = ["bbc.com", "bbc.co.uk"]
-def generate_model(lang, sites, settings, mxParse=100):
+def generate_model(lang, sites, settings, mxParse=10):
     model = LanguageModel(lang)
     mongo = LanguageModel_Mongo("", lang, None)
     parsed = 0
@@ -18,7 +18,11 @@ def generate_model(lang, sites, settings, mxParse=100):
         txt = ' '.join(a.get('text',''))
         adate = ' '.join(a.get('time',''))
         url = ''.join(a.get('url',''))
-        atitle = ' '.join(a.get('title',''))
+        atitle = ""
+        if isinstance(a.get('title', []), list):
+            atitle = ' '.join(a.get('title',''))
+        elif isinstance(a.get('title', ""), basestring):
+            atitle = a.get('title', "")
         for s in sites:
             if s in url:
                 a = Article(text=txt, title=atitle, src=url, date=adate, nid=a['_id'], language_model=model)
@@ -31,4 +35,14 @@ def generate_model(lang, sites, settings, mxParse=100):
     for k, w in model.words.iteritems():
         mongo.__process_word__(w)
 
-generate_model(lang, sites, None, 100)
+    #Update Language Info
+    langInfo = LanguageInfoModel_Mongo()
+
+    keys = sorted(model.words.keys())
+    freq = model.getWordsByFrequency()
+
+    langInfo.updateLanguage(lang, parsed, len(model.words.keys()), sorted(freq.keys())[len(freq)-1], sites)
+
+    return mongo
+
+m = generate_model(lang, sites, None, 10)

### 2015-12-09 textAnalysis/language.py

@@ -45,14 +45,26 @@ class LanguageModel(object):
 
         return flatList
         """
-
-class LanguageModel_Mongo(object):
-    def __init__(self, lang_uri, lang_db, languageModel):
-        self.lang_uri = lang_uri
-        self.lang_db = lang_db
+class LanguageInfoModel_Mongo(object):
+    def __init__(self):
         self.client = pymongo.MongoClient()
         self.db = self.client["text_illustrator"]
-        self.collection = self.db[self.lang_db]
+        self.collection = self.db["language_info"]
+
+    def updateLanguage(self, lang, articleCount=-1, wordCount=-1, mxFreq=-1, sites=[]):
+        entry = {"language":lang.lower(), "articleCount":articleCount, "wordCount":wordCount, "maxFreq":mxFreq, "sites":sites}
+        self.collection.update({"language":lang.lower()}, {"$set":entry}, upsert=True)
+
+    def getLanguage(self, lang):
+        return self.collection.find_one({"language":lang.lower()})
+
+class LanguageModel_Mongo(object):
+    def __init__(self, lang_uri, lang, languageModel):
+        self.lang_uri = lang_uri
+        self.lang = lang
+        self.client = pymongo.MongoClient()
+        self.db = self.client["text_illustrator"]
+        self.collection = self.db[self.lang]
 
     def __load_from_langmodel__(self, languageModel):
         print "Loading language Model"
@@ -77,7 +89,7 @@ class LanguageModel_Mongo(object):
 
     def __update_word__(self, word):
         "update word"
-        wentry = {"word":word.key(), "freq":word.getFreq(), "sub_freq":word.getSubFreq(), "superwords":word.getSuperWords(), "articles":word.getArticlesByRef()}
+        wentry = {"word":word.key(), "word_count":word.word_count, "freq":word.getFreq(), "sub_freq":word.getSubFreq(), "superwords":word.getSuperWords(), "articles":word.getArticlesByRef()}
         self.collection.update_one({"_id":word._id}, {"$set":wentry})
     def __process_word__(self, word):
         "process word"

### 2015-12-09 textAnalysis/word.py

@@ -1,8 +1,9 @@
 #import article
 
 class Word:
-    def __init__(self, word, sub_freq=0, freq=0,superwords=dict()):
+    def __init__(self, word, word_count=1, sub_freq=0, freq=0,superwords=dict()):
         self.word = word.lower()#spelling
+        self.word_count = word_count #for pairs
         self.sub_freq = sub_freq #only relevant if it is an actual word
         self.freq = freq
         self.articles = [] #articles that use this word
@@ -24,6 +25,8 @@ class Word:
     def getSubFreq(self):
         return self.sub_freq
 
+    def articleCount(self):
+        return len(self.articles)
     def getArticlesByRef(self):
         if isinstance(self.articles, dict):
             return self.articles

### 2015-12-09 textAnalysis/article.py
Minor changes.

@@ -182,8 +182,8 @@ class Article(object):
                 wAFreq = wdata.articleCount()
                 #print wdata.articles
                 wOFreq = wdata.getFreq()
-
+                articleSaliencyScore = 1 - float(self.words[w[0]].freq)/float(len(self.words.keys()))
                 if wOFreq < OFreq and wAFreq < AFreq:
-                    ret.append(w[0])
+                    ret.append([w[0], articleSaliencyScore])
 
         return ret

### 2015-12-09 textAnalysis/generate_salient_sets.py

@@ -3,37 +3,35 @@ from article import Article, ArticleDB
 from language import LanguageModel, LanguageModel_Mongo
 
 mxSetSize=1
-lang = "English"
 def get_article(article):
-    txt = ' '.join(a.get('text',''))
-    adate = ' '.join(a.get('time',''))
-    url = ''.join(a.get('url',''))
+    txt = ' '.join(article.get('text',''))
+    adate = ' '.join(article.get('time',''))
+    url = ''.join(article.get('url',''))
     atitle = ""
-    if isinstance(a.get('title', []), list):
-        atitle = ' '.join(a.get('title',''))
-    elif isinstance(a.get('title', ""), basestring):
-        atitle = a.get('title', "")
+    if isinstance(article.get('title', []), list):
+        atitle = ' '.join(article.get('title',''))
+    elif isinstance(article.get('title', ""), basestring):
+        atitle = article.get('title', "")
 
-    return Article(text=txt, title=atitle, src=url, date=adate, nid=a['_id'], language_model=model)
+    return Article(text=txt, title=atitle, src=url, date=adate, nid=article['_id'], language_model=model)
 
 def salient_sets(article_set, model):
     print "Generating Salience Sets..."
     ret = []
-    for a in article_set:
-        article = get_article(a)
+    for aj in article_set:
+        article = get_article(aj)
         article.analyze(mxSetSize, update_model=False)
         ret.append(article.getSalientSets(model.lang))
     print "Finished Generating Salience Sets..."
     return ret
 
 
-model = LanguageModel_Mongo("", lang, None)
+"""
+Example
+
+model = LanguageModel_Mongo("", "English", None)
 articles = ArticleDB()
 
-a = articles.get(0)
-
-ret = salient_sets([a], model)
-
-#for each article
-#get words
-#remove words frequent across articles
+a = [articles.get(0), articles.get(1)]
+ret = salient_sets(a, model)
+"""

### 2015-12-09 textAnalysis/generate_word_list.py

@@ -1,19 +1,16 @@
 from pymongo import MongoClient
 from article import Article, ArticleDB
 from language import LanguageModel, LanguageModel_Mongo, LanguageInfoModel_Mongo
-max_articles = 10
-mxSetSize = 3
-lang = "English"
 #def generate():
 
 sites = ["bbc.com", "bbc.co.uk"]
-def generate_model(lang, sites, settings, mxParse=10):
+def generate_model(lang, sites, settings, mxParse=10, mxSetSize=3):
     model = LanguageModel(lang)
     mongo = LanguageModel_Mongo("", lang, None)
     parsed = 0
 
     articleDB = ArticleDB()
-    while (parsed < mxParse or (max_articles == -1 and articleDB.count())):
+    while (parsed < mxParse or (mxParse == -1 and articleDB.count())):
         a = articleDB.get(index=parsed)
         txt = ' '.join(a.get('text',''))
         adate = ' '.join(a.get('time',''))
@@ -45,4 +42,8 @@ def generate_model(lang, sites, settings, mxParse=10):
 
     return mongo
 
-m = generate_model(lang, sites, None, 10)
+"""
+Example
+
+m = generate_model("English", ["bbc.com", "bbc.co.uk"], None, 10, 3)
+"""

### 2015-12-09 paper/paper.tex
older version

--- 2015-11-14 paper/paper.tex
@@
 In other related studies this task can be done by adding images that appear with a text, but we chose to use google image search to reduce the amount of scraping we need to do to generate our dataset.
+\section{Generate Language Models}
+We include a number of steps for generating language models that each build on each other.
+This allows us to create illustrations at different steps of computation and view the effects of different algorithms.
+\subsection{L1, Frequency and Confidence}
+In our study we create language models for languages of articles that we illustrate.
+We do this using apriori methods and first find frequency for each word and for each set of words with each set being of length N or less.
+We include a settings parameter to allow for the inclusion of splits on choice punctuation marks.
+In this stage we generate frequency overall, and frequency over articles for each word and word pair.
+This stage should be achieved while parsing each article only once.
+
+-Frequency Overall is the sum of the frequency of a given word set in each article for a given language
+-Frequency Over Articles is the number of articles a word appears in for a given language
+
+We expect the least interesting articles would appear the most frequently across articles in any given language.
+In-frequent word sets over all articles that are frequent in a small set of articles are likely to be salient for a given article.
+It is difficult to establish word and word-set salience even with the frequencies.
+Some words may be infrequent and frequent in articles, but not really descriptive of the article in general.
+In using this stage it is necessary to establish
+cut-off points for salient and non-salient word-sets.
+
+\subsection{L1, Possible Extensions}
+A possible extension of L1 is to take into account the time each article is written and published.
+We expect that certain words are more likely to be published during certain time periods of the year such as during holidays (e.g.
+Christmas, Thanksgiving, etc..).
+Also, articles related to a crisis would likely be published during a certain span of time and possibly articles would be published in rememberance of them (e.g.
+911).
+
+\subsection{L2, Sub-words and Word Order}
+In many words their is a tendency for certain word-parts to take a certain order which may vary for a number of reasons such as whether a phrase is a question or statement.
+In the L2 stage we this into account and try to determine whether a language has such an order and when or whether it changes during certain contexts.
+We can determine whether there is a word order by determining if two or more words appear along-side each other relatively frequently.
+
+Another concern about word parts is that certain parts, such as nouns, may be considered more salient for illustration.
+It may be possible to determine whether a particular word is a noun, verb, etc.
+by considering their frequency along-side closely occuring words and their order.
+But, this is a difficult task on its own.
+
+Another consideration is that some languages compound words together or have prefixes and suffixes attached to words in certain contexts. 
+In order for us to determine whether a word occurs within a compound word would be to check whether it appears alone, 
+it's frequency overall (the word 'a' is likely to appear in a lot of words, but it is not a subword), and its frequency as a subword.
+
+\section{Generating Salient Sets}
+Generating salient sets is fairly easy compared with establishing a language model.
+To get a set of salient-words for a given article we provide the L1 statistics for a given article and take the language model for the article.
+We use the article to remove non-salient words from the article and then use a combination of statistics of the word for the article and in the language.
+
+\section{Generating Image Sets}
+In our project we require a large number of images with similar annotations of keywords for each language used.
+The keywords for certain images may differ for each image, but there should be an intersection among the images for a select set of keywords.
+Since this is difficult to obtain on our own we, in our project, turned to google to obtain sets of images for keywords.
+\subsection{I1}
+In I1 we obtain a set of images based on a set of keywords. Among the image sets we would assume that we would 
+be able to generate an intersection of image sets that would be representative of two articles discussing the 
+same thing. Some articles, not in the intersection would be better representative of a given article and even their language. 
+Possibly, we would be able to even find images or sets of images that would represent a difference in how speakers of two different languages
+view the topic or even the words and phrases themselves.
+
+\subsection{I2, Possible extension}
+A possible extension of this stage would be to incorporate machine learning and computer vision to be able to find features and feature-groups within an image.
+Using features and feature-groups we may be able to find which features or feature-groups relate to each keyword or keyword-set and pick images based on this.
+This step is already improved if we are able to match multiple modifications of a single image and throwing away the modified versions.
+Looking at an image on a feature basis allows
+us to generate a better set of images that represent the keywords better.
+
+\section{Generating Illustrations}
+The last and final step in our project is how we visualize the image-sets and the keyword salience.
+Ideally we would be able to combine the images into a single images, but that is a difficult task even if we know what features and feature-groups a keyword or keyword-set occurs too.
+
 \end{document}

### 2015-12-09 paper/paper.tex

@@
 In other related studies this task can be done by adding images that appear with a text, but we chose to use google image search to reduce the amount of scraping we need to do to generate our dataset.
+\section{Generating Relevant Image Set}
+After downloading images from the Google search image API of salient word sets from the article, the common subset of images within these sets must be found.
+This can be done by finding the intersection of all the sets.
+In our implemnetation, we first created subset that was the intersection of two sets and then iteratively performed the intersection of this subset with each other set of images.
+Since the number of images is relatively large, all the images in two sets could not be loaded into memory at once.
+To deal with this issue, the intersection algorithm used was a block-based intersection which loads two blocks of 50 images into memory, then compares each image in 1 block to each image in the other block and output images which are in both blocks.
+To compare the images two different comparison tests were used.
+For two images to be considered the same, they must pass either or both of the comparison tests.
+The first test was a simple pixel by pixel comparison, if for each pixel in each image the values of the pixels were equal then the two images are the same.
+The second comparison test was to take the average colour of all the pixels in a different square regions of the images and compare them.
+If the average colours in each of the regions were the same, then the images are considered the same.
+\section{Problems}
+One problem we encountered was that the Google image seach API only allows for 100 searches per day for free, so gathering enough images for each of the salient sets was impossible.
 \section{Generate Language Models}
@@
 Ideally we would be able to combine the images into a single images, but that is a difficult task even if we know what features and feature-groups a keyword or keyword-set occurs too.
-
 \end{document}

### 2015-12-09 paper/paper.tex
...

@@
 \begin{document}
-\section{Abstract}
-\section{Generating Dataset(s)}
+\section{Introduction}
+Introduction goes here.
+\section{Related Work}
+Related Work
+\subsection{Generating Dataset(s)}
 In our study we created our own dataset(s) in order to generate a dataset containing the data we need.
@@
 In other related studies this task can be done by adding images that appear with a text, but we chose to use google image search to reduce the amount of scraping we need to do to generate our dataset.
-\section{Generating Relevant Image Set}
+\subsection{Generating Relevant Image Set}
 After downloading images from the Google search image API of salient word sets from the article, the common subset of images within these sets must be found.
@@
 If the average colours in each of the regions were the same, then the images are considered the same.
-\section{Problems}
+\subsection{Problems}
 One problem we encountered was that the Google image seach API only allows for 100 searches per day for free, so gathering enough images for each of the salient sets was impossible.
-\section{Generate Language Models}
+\subsection{Generate Language Models}
 We include a number of steps for generating language models that each build on each other.
 This allows us to create illustrations at different steps of computation and view the effects of different algorithms.
-\subsection{L1, Frequency and Confidence}
+\subsubsection{L1, Frequency and Confidence}
 In our study we create language models for languages of articles that we illustrate.
@@
 
-\subsection{L1, Possible Extensions}
+\subsubsection{L1, Possible Extensions}
 A possible extension of L1 is to take into account the time each article is written and published.
@@
 
-\subsection{L2, Sub-words and Word Order}
+\subsubsection{L2, Sub-words and Word Order}
 In many words their is a tendency for certain word-parts to take a certain order which may vary for a number of reasons such as whether a phrase is a question or statement.
@@
 
-\section{Generating Salient Sets}
+\subsection{Generating Salient Sets}
 Generating salient sets is fairly easy compared with establishing a language model.
@@
 
-\section{Generating Image Sets}
+\subsection{Generating Image Sets}
 In our project we require a large number of images with similar annotations of keywords for each language used.
@@
 Since this is difficult to obtain on our own we, in our project, turned to google to obtain sets of images for keywords.
-\subsection{I1}
+\subsubsection{I1}
 In I1 we obtain a set of images based on a set of keywords. Among the image sets we would assume that we would 
@@
 
-\subsection{I2, Possible extension}
+\subsubsection{I2, Possible extension}
 A possible extension of this stage would be to incorporate machine learning and computer vision to be able to find features and feature-groups within an image.
@@
 
-\section{Generating Illustrations}
+\subsection{Generating Illustrations}
 The last and final step in our project is how we visualize the image-sets and the keyword salience.
 Ideally we would be able to combine the images into a single images, but that is a difficult task even if we know what features and feature-groups a keyword or keyword-set occurs too.
+
+\section{Conclusion}
+
+\section{Future Work}
+
 \end{document}

### 2015-12-09 paper/paper.tex
Added introduction and reorganized paper to conform to Carsons layout. Wrote down some notes for different sections.

@@
 \usepackage{lmodern}
+\usepackage{comment}
 \title{Illustrating Text}
@@
 \section{Introduction}
-Introduction goes here.
+%discuss the human link -- the relationship of text and visualization -- motivation
+\paragraph{}
+A text has always been a complicated thing to translate into another language. Language
+is not precise and encoding an idea into text is not always perfect. Often, Language 
+has a number of nuances brought in by different culture. Someone from one country may
+associate luck with red and someone from another country may associate luck with green.
+But, there still will be an intersection in the features, the visualization, of what
+any two people assign to a word or even a text in general. If it was not the case then
+we couldn't translate anything. But, we know that we can translate texts to different
+languages and we know that multiple texts can describe the same thing.
+\paragraph{}
+Often in translation of a text there is some meaning lost. Different cultures view things
+differently and different languages encode ideas differently. Everyone tends to visualize 
+meaning to some extent though.
+
+%define what we are doing in a basic form
+\paragraph{}
+In this paper, we take databases of texts retrieved from sources with different languages and
+cultures. We use the databases, with no prior understanding of the language or cultures, to
+explore whether we can determine a subset of each text and assign it some meaning by obtaining
+images for further subsets of the subset generated for the text. In doing so we expect that
+we can generate meaning for a text and that we can determine whether two texts encode the
+same thing (i.e. \ describe the same event or idea).
+
+%define applications
+\paragraph{}
+Providing translations
+\paragraph{}
+Language learning
+\paragraph{}
+Generating datasetss for related problems
+\paragraph{}
+Organization of Paper \\
+--Related Work \\
+--Basic Method \\
+--Detailed Discussion of Each Step \\
+--Conclusions \\
+--Future Work \\
+--Modification by each step \\
+
 \section{Related Work}
 Related Work
-\subsection{Generating Dataset(s)}
+-- Computer Vision
+
+\section{Basic Method}
+\paragraph{}
+The basic method or principle for the problem is to take or generate a language model for
+each language that is to be used. Then to take a set of texts written in languages that we
+have models for and filter them on some level to generate a set or sets of keywords for each
+text. We then take a model that converts the keywords into a set of images with a similar
+format. Then we perform the very important step of partitioning the images into subsections
+between the languages. We then arrive at the last step where we take the set of images and
+combine them in a meaningful way to illustrate the texts.
+\paragraph{}
+In generating the language model for the languages used, we used basic apriori methods to
+give us relevant data for words and word pairs. Usage of non-aprori methods in way works
+against what we are attempting to do since non-apriori methods may be encoding meaning
+of words or word combinations into account, but we are attempting to solve this through
+the use of images annotated with keywords and phrases. Non-apriori methods may provide
+a better measure of salience then apriori method, but take away from what we are trying
+to explore in a finer grained sense. Ideally we should be able to assign meaning to a text
+without already knowing details of a language as mentioned priori.
+\paragraph{}
+The partitioning of images is the task we would say is the most important step. It is where
+we believe we can take a keyword or phrase, a word part, from one language and assign it a 
+meaning that we can intrinsically understand. Within one language there will be a number of
+sets that are more descriptive of the nuances of the meanings of the keywords within the
+language and others less so. We determine how much a set represents the nuances of a 
+language by seeing if it also exists as a set for another language. The intersection between
+the image sets of two texts acts a way of being able, or a measure, to determine whether or 
+not two texts are two different encodings of the same thing. If the two texts are encoding 
+the same thing, i.e. \ the measure is high, then logically image sets that measure less similar
+are still encoding the same material. But, they are also better encodings for their language
+since they are also incorporating nuances of the language and culture encoding them.
+\paragraph{}
+There are more advanced methods for dealing with image sets that should provide much better
+results and more flexibility in their use. Those methods are discussed at the end of the paper. 
+We felt that usage of simple methods would act as a much better illustration of the problem and
+its difficulty. Our decision to use simpler methods does come with a number of difficulties in
+itself that may not be difficulties of the advanced methods discussed.
+\section{Generating Dataset(s)}
 In our study we created our own dataset(s) in order to generate a dataset containing the data we need.
@@
 In other related studies this task can be done by adding images that appear with a text, but we chose to use google image search to reduce the amount of scraping we need to do to generate our dataset.
-\subsection{Generating Relevant Image Set}
-After downloading images from the Google search image API of salient word sets from the article, the common subset of images within these sets must be found.
-This can be done by finding the intersection of all the sets.
-In our implemnetation, we first created subset that was the intersection of two sets and then iteratively performed the intersection of this subset with each other set of images.
-Since the number of images is relatively large, all the images in two sets could not be loaded into memory at once.
-To deal with this issue, the intersection algorithm used was a block-based intersection which loads two blocks of 50 images into memory, then compares each image in 1 block to each image in the other block and output images which are in both blocks.
-To compare the images two different comparison tests were used.
-For two images to be considered the same, they must pass either or both of the comparison tests.
-The first test was a simple pixel by pixel comparison, if for each pixel in each image the values of the pixels were equal then the two images are the same.
-The second comparison test was to take the average colour of all the pixels in a different square regions of the images and compare them.
-If the average colours in each of the regions were the same, then the images are considered the same.
-\subsection{Problems}
-One problem we encountered was that the Google image seach API only allows for 100 searches per day for free, so gathering enough images for each of the salient sets was impossible.
 \subsection{Generate Language Models}
+\paragraph{}
 We include a number of steps for generating language models that each build on each other.
 This allows us to create illustrations at different steps of computation and view the effects of different algorithms.
-\subsubsection{L1, Frequency and Confidence}
+\paragraph{}
 In our study we create language models for languages of articles that we illustrate.
@@
 
-Another concern about word parts is that certain parts, such as nouns, may be considered more salient for illustration.
-It may be possible to determine whether a particular word is a noun, verb, etc.
-by considering their frequency along-side closely occuring words and their order.
-But, this is a difficult task on its own.
+Another concern about word parts is that certain parts, such as nouns, may be considered more salient for illustration. It may be possible to determine whether a particular word is a noun, verb, etc.
+by considering their frequency along-side closely occuring words and their order. But, this is a difficult task on its own.
 
@@
 Since this is difficult to obtain on our own we, in our project, turned to google to obtain sets of images for keywords.
+
+\subsection{Generating Relevant Image Set}
+After downloading images from the Google search image API of salient word sets from the article, the common subset of images within these sets must be found.
+This can be done by finding the intersection of all the sets.
+In our implemnetation, we first created subset that was the intersection of two sets and then iteratively performed the intersection of this subset with each other set of images.
+Since the number of images is relatively large, all the images in two sets could not be loaded into memory at once.
+To deal with this issue, the intersection algorithm used was a block-based intersection which loads two blocks of 50 images into memory, then compares each image in 1 block to each image in the other block and output images which are in both blocks.
+To compare the images two different comparison tests were used.
+For two images to be considered the same, they must pass either or both of the comparison tests.
+The first test was a simple pixel by pixel comparison, if for each pixel in each image the values of the pixels were equal then the two images are the same.
+The second comparison test was to take the average colour of all the pixels in a different square regions of the images and compare them.
+If the average colours in each of the regions were the same, then the images are considered the same.
+
 \subsubsection{I1}
@@
 
-\subsubsection{I2, Possible extension}
+\subsection{Generating Illustrations}
+The last and final step in our project is how we visualize the image-sets and the keyword salience.
+Ideally we would be able to combine the images into a single images, but that is a difficult task even if we know what features and feature-groups a keyword or keyword-set occurs too.
+
+\section{Conclusion and Problems}
+-- better datasets needed
+
+\subsection{Problems}
+One problem we encountered was that the Google image seach API only allows for 100 searches per day for free, so gathering enough images for each of the salient sets was impossible.
+
+\section{Future Work}
+-- better datasets (particularly for images)
+-- more complex analysis of images
+-- break down of images into features and feature groups
+
+\subsection{Modelling a Language}
+-- use non-apriori methods
+-- user generated keywords and machine learning
+-- more complex apriori methods
+
+\subsection{Image Dataset}
+-- Create custom dataset by crowd-sourcing or move intensive data-mining for reuse of images
+
+\subsection{Image Analysis and Partitioning of Image Sets}
 A possible extension of this stage would be to incorporate machine learning and computer vision to be able to find features and feature-groups within an image.
@@
 
-\subsection{Generating Illustrations}
-The last and final step in our project is how we visualize the image-sets and the keyword salience.
-Ideally we would be able to combine the images into a single images, but that is a difficult task even if we know what features and feature-groups a keyword or keyword-set occurs too.
-
-\section{Conclusion}
-
-\section{Future Work}
+\subsection{Illustration}
+-- Composite Images based on keywords
+-- Exploration of culturally ambiguous collages (Left-to-Right Right-to-Left)
+-- Image Modification based Salience and Computer Vision
 

### 2015-12-10 paper/paper.tex
minor changes to textAnalysis and much more progress on the paper. Biggest thing to do is the related work and bringing in some images from the program.

--- 2015-12-09 paper/paper.tex
@@
 \usepackage{lmodern}
+\usepackage{comment}
 \title{Illustrating Text}
 \author{Christopher Catton, Partick Murphy, Charles Ung}
+\date{December 10, 2015}
 \begin{document}
-\section{Abstract}
-\section{Generating Dataset(s)}
-In our study we created our own dataset(s) in order to generate a dataset containing the data we need.
-We generated the dataset by crawling and scraping separate news sites.
-These new sites include the British Broadcasting Corporation, the New York Times, De Telegraaf, and De Volkskrant.
-Our data is tuple of the source, date, and text of an article.
-Instead of gathering data related to images, we use google image search to generate a set of images related to a set and subsets of the words we extract from a text.
-In other related studies this task can be done by adding images that appear with a text, but we chose to use google image search to reduce the amount of scraping we need to do to generate our dataset.
-\section{Generating Relevant Image Set}
-After downloading images from the Google search image API of salient word sets from the article, the common subset of images within these sets must be found.
-This can be done by finding the intersection of all the sets.
-In our implemnetation, we first created subset that was the intersection of two sets and then iteratively performed the intersection of this subset with each other set of images.
-Since the number of images is relatively large, all the images in two sets could not be loaded into memory at once.
-To deal with this issue, the intersection algorithm used was a block-based intersection which loads two blocks of 50 images into memory, then compares each image in 1 block to each image in the other block and output images which are in both blocks.
-To compare the images two different comparison tests were used.
-For two images to be considered the same, they must pass either or both of the comparison tests.
-The first test was a simple pixel by pixel comparison, if for each pixel in each image the values of the pixels were equal then the two images are the same.
-The second comparison test was to take the average colour of all the pixels in a different square regions of the images and compare them.
-If the average colours in each of the regions were the same, then the images are considered the same.
-\section{Problems}
-One problem we encountered was that the Google image seach API only allows for 100 searches per day for free, so gathering enough images for each of the salient sets was impossible.
+\maketitle
+\section{Introduction}
+%discuss the human link -- the relationship of text and visualization -- motivation
+\paragraph{}
+A text has always been a complicated thing to translate into another language. Language
+is not precise and encoding an idea into text is not always perfect. Often, Language 
+has a number of nuances brought in by different culture. Someone from one country may
+associate luck with red and someone from another country may associate luck with green.
+But, there still will be an intersection in the features, the visualization, of what
+any two people assign to a word or even a text in general. If it was not the case then
+we couldn't translate anything. But, we know that we can translate texts to different
+languages and we know that multiple texts can describe the same thing.
+\paragraph{}
+Often in translation of a text there is some meaning lost. Different cultures view things
+differently and different languages encode ideas differently. Everyone tends to visualize 
+meaning to some extent though.
+
+%define what we are doing in a basic form
+\paragraph{}
+In this paper, we take databases of texts retrieved from sources with different languages and
+cultures. We use the databases, with no prior understanding of the language or cultures, to
+explore whether we can determine a subset of each text and assign it some meaning by obtaining
+images for further subsets of the subset generated for the text. In doing so we expect that
+we can generate meaning for a text and that we can determine whether two texts encode the
+same thing (i.e. \ describe the same event or idea).
+
+%define applications
+\paragraph{}
+An interesting, but difficult application for this problem is to generate visual translations. 
+Providing an image for a small set of texts can aide in translation or even language learning
+tasks, but it is dificult to illustrate certain language elements. Take for example elements
+such as `a', `but', `or', or even `context'. There are a lot of elements that may not be 
+easily transcribed into an image, but others such as `man', `woman', and `building' could
+easily be transcribed. There are also more complex elements that can be described such as
+the word `luck' or `lottery'. There are difficulties in any approach to translate and 
+teaching languages and we believe that generating visual illustrations as we attempt to do 
+is a possible application.
+
+\paragraph{}
+Generating datasetss for related problems
+Another application is generating datasets for other related problems such as trying to 
+describe a given image. The task has been tried before and this could potentially generate
+a dataset for training a neural network for doing the task. This probably could be best 
+achieved by building a dataset for training an object recognition network. In the simplest
+form of the problem we are setting out to achieve could result in providing a set of collages
+with images keyed to a certain location in each matrix produced from a keyword/phrase set.
+
+\paragraph{}
+There are many facets to the given problem and this paper is organize to partition each step. This
+paper first discusses the basic method of acheiving results and then details each step. The details
+are then followed by our conclusions of our exploration. The last section is a discussion on what 
+can be done to improve our results and what modifications can be done to create more complex, 
+interesting, and generally better performing models.
+
+\section{Related Work}
+Related Work
+-- Computer Vision
+
+\section{Basic Method}
+
+\paragraph{}
+The basic method or principle for the problem is to take or generate a language model for
+each language that is to be used. Then to take a set of texts written in languages that we
+have models for and filter them on some level to generate a set or sets of keywords for each
+text. We then take a model that converts the keywords into a set of images with a similar
+format. Then we perform the very important step of partitioning the images into subsections
+between the languages. We then arrive at the last step where we take the set of images and
+combine them in a meaningful way to illustrate the texts.
+
+\paragraph{}
+In generating the language model for the languages used, we used basic apriori methods to
+give us relevant data for words and word pairs. Usage of non-aprori methods in way works
+against what we are attempting to do since non-apriori methods may be encoding meaning
+of words or word combinations into account, but we are attempting to solve this through
+the use of images annotated with keywords and phrases. Non-apriori methods may provide
+a better measure of salience then apriori method, but take away from what we are trying
+to explore in a finer grained sense. Ideally we should be able to assign meaning to a text
+without already knowing details of a language as mentioned priori.
+
+\paragraph{}
+The partitioning of images is the task we would say is the most important step. It is where
+we believe we can take a keyword or phrase, a word part, from one language and assign it a 
+meaning that we can intrinsically understand. Within one language there will be a number of
+sets that are more descriptive of the nuances of the meanings of the keywords within the
+language and others less so. We determine how much a set represents the nuances of a 
+language by seeing if it also exists as a set for another language. The intersection between
+the image sets of two texts acts a way of being able, or a measure, to determine whether or 
+not two texts are two different encodings of the same thing. If the two texts are encoding 
+the same thing, i.e. \ the measure is high, then logically image sets that measure less similar
+are still encoding the same material. But, they are also better encodings for their language
+since they are also incorporating nuances of the language and culture encoding them.
+
+\paragraph{}
+There are more advanced methods for dealing with image sets that should provide much better
+results and more flexibility in their use. Those methods are discussed at the end of the paper. 
+We felt that usage of simple methods would act as a much better illustration of the problem and
+its difficulty. Our decision to use simpler methods does come with a number of difficulties in
+itself that may not be difficulties of the advanced methods discussed.
+
+\section{Generating Language Model Dataset(s)}
+In our study we created our own dataset(s) in order to generate a dataset containing the data we 
+need. We generated the dataset by crawling and scraping separate news sites. These new sites 
+include the British Broadcasting Corporation, the New York Times, De Telegraaf, and De Volkskrant. 
+Our data is tuple of the source, date, and text of an article. Instead of gathering data related 
+to images, we use google image search to generate a set of images related to a set and subsets of 
+the words we extract from a text. In other related studies this task can be done by adding images 
+that appear with a text, but we chose to use google image search to reduce the amount of scraping 
+we need to do to generate our dataset.
+
 \section{Generate Language Models}
-We include a number of steps for generating language models that each build on each other.
-This allows us to create illustrations at different steps of computation and view the effects of different algorithms.
-\subsection{L1, Frequency and Confidence}
-In our study we create language models for languages of articles that we illustrate.
-We do this using apriori methods and first find frequency for each word and for each set of words with each set being of length N or less.
-We include a settings parameter to allow for the inclusion of splits on choice punctuation marks.
-In this stage we generate frequency overall, and frequency over articles for each word and word pair.
-This stage should be achieved while parsing each article only once.
 
--Frequency Overall is the sum of the frequency of a given word set in each article for a given language
--Frequency Over Articles is the number of articles a word appears in for a given language
+\paragraph{}
+In our study we create language models for languages of articles that we illustrate. We do this using 
+apriori methods and first find frequency for each word and for each set of words with each set being 
+of length N or less. We automatically remove punctuation marks and split on each space and parse each
+word as part of sets between the size of 1 < N, with N being the max set size. Each set is constructed
+with words found by each other. This is the stage we generate frequency overall, and frequency over 
+articles for each word and word pair. This stage should be achieved while parsing each article only once.
 
-We expect the least interesting articles would appear the most frequently across articles in any given language.
-In-frequent word sets over all articles that are frequent in a small set of articles are likely to be salient for a given article.
-It is difficult to establish word and word-set salience even with the frequencies.
-Some words may be infrequent and frequent in articles, but not really descriptive of the article in general.
-In using this stage it is necessary to establish
-cut-off points for salient and non-salient word-sets.
+\paragraph{}
+In more detail, we select a number of sites that are written in a specific language and parse the articles
+we have already obtained in generating our dataset. Each Article is then processed to obtain the frequency
+for each word and phrase of an appropriate size. After each Article is parsed its words and statistics are
+added to the language model.
 
-\subsection{L1, Possible Extensions}
-A possible extension of L1 is to take into account the time each article is written and published.
-We expect that certain words are more likely to be published during certain time periods of the year such as during holidays (e.g.
-Christmas, Thanksgiving, etc..).
-Also, articles related to a crisis would likely be published during a certain span of time and possibly articles would be published in rememberance of them (e.g.
-911).
+\paragraph{}
+We expect the least interesting articles would appear the most frequently across articles in any given 
+language. In-frequent word sets over all articles that are frequent in a small set of articles are likely 
+to be salient for a given article. It is difficult to establish word and word-set salience even with the 
+frequencies. Some words may be infrequent and frequent in articles, but not really descriptive of the 
+article in general. In using this stage it is necessary to establish cut-off points for salient and 
+non-salient word-sets.
 
-\subsection{L2, Sub-words and Word Order}
-In many words their is a tendency for certain word-parts to take a certain order which may vary for a number of reasons such as whether a phrase is a question or statement.
-In the L2 stage we this into account and try to determine whether a language has such an order and when or whether it changes during certain contexts.
-We can determine whether there is a word order by determining if two or more words appear along-side each other relatively frequently.
+\section{Generating Salient Keyword/Phrase Sets}
+Generating salient sets is fairly easy compared with establishing a language model. To get a set of 
+salient-words for a given article we provide the statistics for a given article and take the language 
+model for the article. We use the language model to remove non-salient words from the article and then 
+use some combination of statistics of the word for the article and in the language. It is hard to
+determine a good combination of the statistics that represent the salience of a given word or word-set. 
+Determining a statistic that represents good salience for a word or word-set is a problem on its own.
+\paragraph{}
+In this paper we choose a the combination:
+$$1-frequencyInArticle(Word)/numberOfWordsInArticle$$
+to represent the salience of a word or word-set.
+\paragraph{}
+We also use two thresholds to remove non-salient words. One is the percent of articles that a word or
+word-set appears in and the other is how many occurences does the word appear overall.
 
-Another concern about word parts is that certain parts, such as nouns, may be considered more salient for illustration.
-It may be possible to determine whether a particular word is a noun, verb, etc.
-by considering their frequency along-side closely occuring words and their order.
-But, this is a difficult task on its own.
+\section{Generating Image Sets}
+In our project we require a large number of images with similar annotations of keywords for each language 
+used. The keywords for certain images may differ for each image, but there should be an intersection among 
+the images for a select set of keywords. Since this is difficult to obtain on our own we, in our project, 
+turned to google to obtain sets of images for keywords.
+\paragraph{}
+In generating a number of seperate sets for each set of salient keyword/phrase sets, we hope to be able
+to determine whether there are any sets, generated by different texts, that are similar enough to be
+considered the same. If they are similar enough it follows that the texts are encoding the same material 
+and we can possibly say that if the articles are in different languages then they are approximate 
+translations of each other.
+\paragraph{}
+After downloading images from the Google search image API of salient word sets from the article, the common 
+subset of images within these sets must be found. This can be done by finding the intersection of all the 
+sets. In our implemnetation, we first created subset that was the intersection of two sets and then 
+iteratively performed the intersection of this subset with each other set of images. Since the number of 
+images is relatively large, all the images in two sets could not be loaded into memory at once. To deal with 
+this issue, the intersection algorithm used was a block-based intersection which loads two blocks of 50 images 
+into memory, then compares each image in 1 block to each image in the other block and output images which are 
+in both blocks. To compare the images two different comparison tests were used. For two images to be considered 
+the same, they must pass either or both of the comparison tests. The first test was a simple pixel by pixel 
+comparison, if for each pixel in each image the values of the pixels were equal then the two images are the 
+same. The second comparison test was to take the average colour of all the pixels in a different square regions 
+of the images and compare them. If the average colours in each of the regions were the same, then the images 
+are considered the same.
 
+\section{Generating Illustrations}
+The last and final step in our project is how we visualize the image-sets and the keyword salience. Ideally we 
+would be able to combine the images into a single images, but that is a difficult task even if we know what 
+features and feature-groups a keyword or keyword-set relates to. Instead we opted for creating collage of the 
+images within a set. This means that we would generate something similar to what one might expect an output of 
+a model for object segmentation. There are no masks of objects, but we might expect that certain positions in 
+a matrix to be occupied by a certain object for a salient set.
+\paragraph{}
+In arranging images in a collage we get around the problem of trying to combine them and possibly provide 
+something in way of a story arc. It should show more meaningful visualization of the article at the origin of 
+the matrix then in other places, provided that the salience measure is correct. It is also fairly culturally 
+ambiguous since a lot of cultures have come to expect items to start in the top-left in recent times. But, 
+there are more culturally ambiguous ways to create illustrations as well (which are more difficult).
+
+\section{Conclusion and Problems}
+One problem we encountered was that the Google image seach API only allows for 100 searches per day for free, so 
+gathering enough images for each of the salient sets was impossible. This in turn has made it impossible to 
+get the results we would consider significant. To obtain the results we want we will need access to a database 
+that we can obtain a much larger set of images for each salient set. This may be achieved by data-mining for
+images based on the salient sets themselves. Though there are possible ways of reducing the requirement of a
+large amount of images which are discussed later.
+\paragraph{}
+Another problem is validation of results. Since we were unable to obtain the results needed, it is not relevant
+that we cannot evaluate them. But, it needs to be discussed how we would go about evaluating the results had 
+we obtained them. For this task we probably we need to crowd-source in order to have people evaluate the accuracy 
+of the results. It isn't out of ordinary to need actual people to be involved the actual evaluation of the results. 
+In computer vision a lot of data for evaluating models for generating salience or object segmentation have manually 
+generated data from people. For us, we would not need any special tools such as eye-tracking tools to determine 
+the accuracy though.
+
+\section{Future Work}
+-- better datasets (particularly for images)
+-- more complex analysis of images
+-- break down of images into features and feature groups
+
+\subsection{Datasets}
+Future work needs access to a larger set of images annotated with keywords and phrases. It may be necessary to mine 
+for the images and annotations specifically or to crowd source the annotations of mined images. But, it is achievable 
+and may provide the results we wished to achieve. One issue we found with google is that the search, provided with two 
+words that are nearly identical in meaning, does not provide nearly identical results. Ideally images would have 
+similar ranking in a search for words with a similar meaning. We went in expecting there to be a large reuse of images 
+between people of different language groups, but our observations now point us in a different direction.
+
+\subsection{Language Model}
+A possible extension of how we generate a language model is to take into account the time each article is written and 
+published. We expect that certain words are more likely to be published during certain time periods of the year such as 
+during holidays (e.g. Christmas, Thanksgiving). Also, articles related to a crisis would likely be published during a 
+certain span of time and possibly articles would be published in rememberance of them (e.g. 911).
+\paragraph{}
+In many languages their is a tendency for certain word-parts to take a certain order which may vary for a number of 
+reasons such as whether a phrase is a question or statement. In later iterations of our language model we can take 
+this into account and try to determine whether a language has such an order and when or whether it changes during 
+certain contexts. We can determine whether there is a word order by determining if two or more words appear 
+along-side each other relatively frequently.
+\paragraph{}
+Another concern about word-parts is that certain parts, such as nouns, may be considered more salient for illustration. 
+It may be possible to determine whether a particular word is a noun, verb, etc. \ by considering their frequency 
+along-side closely occuring words and their order. But, this is a difficult task on its own.
+\paragraph{}
 Another consideration is that some languages compound words together or have prefixes and suffixes attached to words in certain contexts. 
 In order for us to determine whether a word occurs within a compound word would be to check whether it appears alone, 
-it's frequency overall (the word 'a' is likely to appear in a lot of words, but it is not a subword), and its frequency as a subword.
+it's frequency overall (the word `a' is likely to appear in a lot of words, but it is not a subword), and its frequency as a subword.
+\paragraph{}
+The task of getting relevant salient sets of words isn't necessarily resrticed to apriori methods or even traditional 
+data-mining techniques. In a way using non-apriori methods may detract from ascertaining the meaning from the image sets 
+we find. But, their results could still be considered interesting and relevant. It would be an interesting task to design 
+a neural network to determine word salience or even to get it to create the illustrations. Some machine learning and a 
+training set to determine thresholds for what is and is not salient could go a long ways. The thresholds would probably 
+maintain relevance across different methods of solving the problem, but right now we are only guessing and manually 
+adjusting them.
 
-\section{Generating Salient Sets}
-Generating salient sets is fairly easy compared with establishing a language model.
-To get a set of salient-words for a given article we provide the L1 statistics for a given article and take the language model for the article.
-We use the article to remove non-salient words from the article and then use a combination of statistics of the word for the article and in the language.
+\subsection{Image Analysis and Partitioning of Image Sets}
+A possible extension of this stage would be to incorporate machine learning and computer vision to be able to find 
+features and feature-groups within an image. Using features and feature-groups we may be able to find which features 
+or feature-groups relate to each keyword or keyword-set and pick images based on this. This step is already improved 
+if we are able to match multiple modifications of a single image and throwing away the modified versions. Looking at 
+an image on a feature basis allows us to generate a better set of images that represent the keywords better.
 
-\section{Generating Image Sets}
-In our project we require a large number of images with similar annotations of keywords for each language used.
-The keywords for certain images may differ for each image, but there should be an intersection among the images for a select set of keywords.
-Since this is difficult to obtain on our own we, in our project, turned to google to obtain sets of images for keywords.
-\subsection{I1}
-In I1 we obtain a set of images based on a set of keywords. Among the image sets we would assume that we would 
-be able to generate an intersection of image sets that would be representative of two articles discussing the 
-same thing. Some articles, not in the intersection would be better representative of a given article and even their language. 
-Possibly, we would be able to even find images or sets of images that would represent a difference in how speakers of two different languages
-view the topic or even the words and phrases themselves.
+\subsection{Illustration}
+-- Composite Images based on keywords
+-- Exploration of culturally ambiguous collages (Left-to-Right Right-to-Left)
+-- Image Modification based Salience and Computer Vision
 
-\subsection{I2, Possible extension}
-A possible extension of this stage would be to incorporate machine learning and computer vision to be able to find features and feature-groups within an image.
-Using features and feature-groups we may be able to find which features or feature-groups relate to each keyword or keyword-set and pick images based on this.
-This step is already improved if we are able to match multiple modifications of a single image and throwing away the modified versions.
-Looking at an image on a feature basis allows
-us to generate a better set of images that represent the keywords better.
-
-\section{Generating Illustrations}
-The last and final step in our project is how we visualize the image-sets and the keyword salience.
-Ideally we would be able to combine the images into a single images, but that is a difficult task even if we know what features and feature-groups a keyword or keyword-set occurs too.
 \end{document}

### 2015-12-10 textAnalysis/article.py

@@ -145,7 +145,7 @@ class Article(object):
             if len(wset) >= mxSize:
                 temp = wset[1:mxSize]
                 wset = temp
-            elif w != '' and w != ' ':
+            elif w != '' and w != ' ' and w.isdigit() == False:
                 wset.append(w)
 
                 for i in range(1, len(wset)+1):

### 2015-12-10 textAnalysis/generate_salient_sets.py

@@ -2,7 +2,7 @@ from pymongo import MongoClient
 from article import Article, ArticleDB
 from language import LanguageModel, LanguageModel_Mongo
 
-mxSetSize=1
+#mxSetSize=1
 def get_article(article):
     txt = ' '.join(article.get('text',''))
     adate = ' '.join(article.get('time',''))
@@ -15,7 +15,7 @@ def get_article(article):
 
     return Article(text=txt, title=atitle, src=url, date=adate, nid=article['_id'], language_model=model)
 
-def salient_sets(article_set, model):
+def salient_sets(article_set, model, mxSetSize=2):
     print "Generating Salience Sets..."
     ret = []
     for aj in article_set:
@@ -26,12 +26,12 @@ def salient_sets(article_set, model):
     return ret
 
 
-"""
-Example
+
+#Example
 
 model = LanguageModel_Mongo("", "English", None)
 articles = ArticleDB()
 
 a = [articles.get(0), articles.get(1)]
 ret = salient_sets(a, model)
-"""
+

### 2015-12-10 textAnalysis/generate_word_list.py

@@ -4,13 +4,13 @@ from language import LanguageModel, LanguageModel_Mongo, LanguageInfoModel_Mongo
 #def generate():
 
 sites = ["bbc.com", "bbc.co.uk"]
-def generate_model(lang, sites, settings, mxParse=10, mxSetSize=3):
+def generate_model(lang, sites, settings, mxParse=-1, mxSetSize=3):
     model = LanguageModel(lang)
     mongo = LanguageModel_Mongo("", lang, None)
     parsed = 0
 
     articleDB = ArticleDB()
-    while (parsed < mxParse or (mxParse == -1 and articleDB.count())):
+    while (parsed < mxParse or (mxParse == -1 and parsed < articleDB.count())):
         a = articleDB.get(index=parsed)
         txt = ' '.join(a.get('text',''))
         adate = ' '.join(a.get('time',''))
@@ -44,6 +44,5 @@ def generate_model(lang, sites, settings, mxParse=10, mxSetSize=3):
 
 """
 Example
-
-m = generate_model("English", ["bbc.com", "bbc.co.uk"], None, 10, 3)
 """
+m = generate_model("English", ["bbc.com", "bbc.co.uk"], None, -1, 2)

### 2015-12-10 paper/paper.tex
Mostly done. Need to write related work section and add data produced by code

@@
 \section{Future Work}
--- better datasets (particularly for images)
--- more complex analysis of images
--- break down of images into features and feature groups
-
 \subsection{Datasets}
@@
 if we are able to match multiple modifications of a single image and throwing away the modified versions. Looking at 
-an image on a feature basis allows us to generate a better set of images that represent the keywords better.
+an image on a feature basis allows us to generate a better set of images that represent the keywords better and means 
+that we possibly won't need to have as large of a database of images with similar keyword/phrase annotations.
+\paragraph{}
+Learning to relate features and feature-groups to keywords and keyphrases can be done independently for each language. 
+It may be possible to completely get around a need for a single database of images with keyword/phrase annotations 
+for all languages. This would be the best modification to our project and product the best results. One of the biggest 
+problems is the database for the images.
 
 \subsection{Illustration}
--- Composite Images based on keywords
--- Exploration of culturally ambiguous collages (Left-to-Right Right-to-Left)
--- Image Modification based Salience and Computer Vision
-
+The step of creating the illustration can be modified in a number of ways. The best method likely varies based on what 
+you want to use the results for. For language learning and depending on the text size, it is probably best to either 
+find a single image that is representitive of the salient set it represents or to be able to combine the images or 
+features related to the keywords into an image. In some cases it probably would be best to have a series of images 
+to represent a meaning. Illustrating certain actions would probably require multiple images to be accuratley 
+illustrated.
 \end{document}

### 2015-12-10 textAnalysis/article.py
fixed issue with genWordSets in article.

@@ -145,11 +145,11 @@ class Article(object):
             if len(wset) >= mxSize:
                 temp = wset[1:mxSize]
                 wset = temp
-            elif w != '' and w != ' ' and w.isdigit() == False:
+            if w != '' and w != ' ' and w.isdigit() == False:
                 wset.append(w)
 
                 for i in range(1, len(wset)+1):
-                    yield [' '.join(wset[0:i]), i]
+                    yield [' '.join(wset[0:i]).lower(), i]
 
     def getSalientSets(self, lang, mxSetSize=1, AFreqP=0.20, OFreqP=0.0625):
         sets = dict()
@@ -178,12 +178,10 @@ class Article(object):
         for w in self.genWordSets(mxSetSize):
             wdata = self.language_model.getWord(w[0])
             if wdata != None:
-                #print "TEST ", w
                 wAFreq = wdata.articleCount()
-                #print wdata.articles
                 wOFreq = wdata.getFreq()
                 articleSaliencyScore = 1 - float(self.words[w[0]].freq)/float(len(self.words.keys()))
                 if wOFreq < OFreq and wAFreq < AFreq:
                     ret.append([w[0], articleSaliencyScore])
 
-        return ret
+        return [ret, self]

### 2015-12-10 textAnalysis/generate_salient_sets.py

@@ -21,6 +21,7 @@ def salient_sets(article_set, model, mxSetSize=2):
     for aj in article_set:
         article = get_article(aj)
         article.analyze(mxSetSize, update_model=False)
+        #ret.append(article)
         ret.append(article.getSalientSets(model.lang))
     print "Finished Generating Salience Sets..."
     return ret
@@ -28,10 +29,10 @@ def salient_sets(article_set, model, mxSetSize=2):
 
 
 #Example
-
+"""
 model = LanguageModel_Mongo("", "English", None)
 articles = ArticleDB()
 
 a = [articles.get(0), articles.get(1)]
 ret = salient_sets(a, model)
-
+"""

### 2015-12-10 textAnalysis/generate_salient_sets.py
minor change

@@ -2,7 +2,6 @@ from pymongo import MongoClient
 from article import Article, ArticleDB
 from language import LanguageModel, LanguageModel_Mongo
 
-#mxSetSize=1
 def get_article(article):
     txt = ' '.join(article.get('text',''))
     adate = ' '.join(article.get('time',''))
@@ -15,14 +14,14 @@ def get_article(article):
 
     return Article(text=txt, title=atitle, src=url, date=adate, nid=article['_id'], language_model=model)
 
-def salient_sets(article_set, model, mxSetSize=2):
+def salient_sets(article_set, model, mxSetSize=2, AFreqP=0.05, OFreqP=0.03125):
     print "Generating Salience Sets..."
     ret = []
     for aj in article_set:
         article = get_article(aj)
         article.analyze(mxSetSize, update_model=False)
         #ret.append(article)
-        ret.append(article.getSalientSets(model.lang))
+        ret.append(article.getSalientSets(model.lang, mxSetSize, AFreqP, OFreqP))
     print "Finished Generating Salience Sets..."
     return ret
 
@@ -36,3 +35,4 @@ articles = ArticleDB()
 a = [articles.get(0), articles.get(1)]
 ret = salient_sets(a, model)
 """
+

### 2015-12-10 datacollecter/datacollecter/spiders/bbc_spider.py
added url to nytimes items

@@ -6,7 +6,7 @@ class BbcSpider(scrapy.Spider):
     # Name must be specified outside of the constructor in order to be able to crawl using this spider
     name = "bbc"
     max_articles = 2000
-    
+
     def __init__(self, *args):
         self.allowed_domains = ["bbc.com", "bbc.co.uk"]
         self.start_urls = ["http://www.bbc.com"]
@@ -22,16 +22,16 @@ class BbcSpider(scrapy.Spider):
         }
 
         self.article_count = 0
-    
+
         scrapy.Spider.__init__(self, *args)
-    
+
     def parse(self, response):
         articles_on_page = response.xpath("//a//@href")
         for article_url in articles_on_page:
             if self.news_re.match(article_url.extract()):
                 full_article_url = response.urljoin(article_url.extract())
                 yield scrapy.Request(full_article_url, callback=self.parse_article)
-    
+
     def parse_article(self, response):
         # Only works for specific sections
         if self.crawler.stats.get_value('pages_crawled') < self.max_articles:
@@ -41,7 +41,7 @@ class BbcSpider(scrapy.Spider):
                     if article_item:
                         self.crawler.stats.inc_value('pages_crawled')
                         yield article_item
-        
+
             articles_on_page = response.xpath("//a//@href")
             for article_url in articles_on_page:
                 if self.news_re.match(article_url.extract()):
@@ -50,25 +50,25 @@ class BbcSpider(scrapy.Spider):
                         if invalid_re.match(article_url.extract()):
                             invalid = True
                             break
-                            
+
                     if invalid:
                         continue
-                            
+
                     if self.crawler.stats.get_value('pages_crawled') < self.max_articles:
                         full_article_url = response.urljoin(article_url.extract())
                         yield scrapy.Request(full_article_url, callback=self.parse_article)
-        
+
     def parse_world_article(self, response):
         title = response.xpath("//h1[@class = 'story-body__h1']//text()[1]").extract()
         text = response.xpath("//div[@class ='story-body']//p//text()").extract()
-        
+
         # Ensure there is a title for the articles
         if len(title) == 0:
             return None
-        
+
         article_item = datacollecter.items.ArticleItem()
         article_item['title'] = title[0]
         article_item['text'] = text
         article_item['url'] = response.url
         return article_item
-        
+

### 2015-12-10 datacollecter/datacollecter/spiders/nytimes_spider.py

@@ -10,44 +10,45 @@ class NyTimesSpider(scrapy.Spider):
     invalid_res = [
         re.compile('.*\/travel\/.*'),
     ]
-    
+
     def parse(self, response):
         # Get the top news story links
         article_item = self.parse_article(response)
         if article_item is not None and self.crawler.stats.get_value('pages_crawled') < self.max_articles:
             self.crawler.stats.inc_value('pages_crawled')
             yield article_item
-        
+
         articles_on_page = response.xpath("//a//@href")
         for article in articles_on_page:
             if self.crawler.stats.get_value('pages_crawled') < self.max_articles:
                 full_article_url = response.urljoin(article.extract())
-                
+
                 invalid = False
                 for invalid_re in self.invalid_res:
                     if invalid_re.match(full_article_url):
                         invalid = True
                         break
-                        
+
                 if invalid:
                     yield scrapy.Request(full_article_url, callback=self.parse)
-        
+
     def parse_article(self, response):
         # Only want the h1 story-headings, so story links on the page are not accidentally pulled as well
         utf8_title = ' '.join(response.xpath("//h1[@id = 'story-heading']//text()").extract())
         title = self.__remove_non_ascii_chars(utf8_title)
-        
+
         if title is None:
             return None
-        
+
         # Ignore articles with no title, a few links to non-article pages are being returned and I'm not sure why
         if len(title) >= 1:
             utf8_text = '\n'.join(response.xpath("//article[@id = 'story']//p[@class = 'story-body-text story-content']//text()").extract())
             text = self.__remove_non_ascii_chars(utf8_text)
-            
+
             article_item = datacollecter.items.ArticleItem()
             article_item['title'] = title
             article_item['text'] = text
+            article_item['url'] = response.url
             return article_item
         return None
 

### 2015-12-10 textAnalysis/generate_salient_sets.py
commented out example usage

@@ -3,9 +3,18 @@ from article import Article, ArticleDB
 from language import LanguageModel, LanguageModel_Mongo
 
 def get_article(article):
-    txt = ' '.join(article.get('text',''))
+    txt = ""#' '.join(article.get('text',''))
     adate = ' '.join(article.get('time',''))
-    url = ''.join(article.get('url',''))
+    url = ""# ''.join(article.get('url',''))
+
+    if isinstance(article.get('url', []), list):
+        url = ' '.join(article.get('url',''))
+    elif isinstance(article.get('url', ""), basestring):
+        url = article.get('url', "")
+    if isinstance(article.get('text', []), list):
+        txt = ' '.join(article.get('text',''))
+    elif isinstance(article.get('text', ""), basestring):
+        txt = article.get('text', "")
     atitle = ""
     if isinstance(article.get('title', []), list):
         atitle = ' '.join(article.get('title',''))
@@ -14,7 +23,7 @@ def get_article(article):
 
     return Article(text=txt, title=atitle, src=url, date=adate, nid=article['_id'], language_model=model)
 
-def salient_sets(article_set, model, mxSetSize=2, AFreqP=0.05, OFreqP=0.03125):
+def salient_sets(article_set, model, mxSetSize=2, AFreqP=0.001565, OFreqP=0.001565):
     print "Generating Salience Sets..."
     ret = []
     for aj in article_set:
@@ -29,10 +38,10 @@ def salient_sets(article_set, model, mxSetSize=2, AFreqP=0.05, OFreqP=0.03125):
 
 #Example
 """
+n = 0.5**10
 model = LanguageModel_Mongo("", "English", None)
 articles = ArticleDB()
 
 a = [articles.get(0), articles.get(1)]
-ret = salient_sets(a, model)
+ret = salient_sets(a, model, 1, n, n)
 """
-

### 2015-12-10 textAnalysis/generate_word_list.py

@@ -12,10 +12,19 @@ def generate_model(lang, sites, mxParse=-1, mxSetSize=3):
     articleDB = ArticleDB()
     while (parsed < mxParse or (mxParse == -1 and parsed < articleDB.count())):
         a = articleDB.get(index=parsed)
-        txt = ' '.join(a.get('text',''))
+        txt = ""#' '.join(a.get('text',''))
         adate = ' '.join(a.get('time',''))
-        url = ''.join(a.get('url',''))
+        url = ""#''.join(a.get('url',''))
         atitle = ""
+
+        if isinstance(a.get('url', []), list):
+            url = ' '.join(a.get('url',''))
+        elif isinstance(a.get('url', ""), basestring):
+            url = a.get('url', "")
+        if isinstance(a.get('text', []), list):
+            txt = ' '.join(a.get('text',''))
+        elif isinstance(a.get('text', ""), basestring):
+            txt = a.get('text', "")
         if isinstance(a.get('title', []), list):
             atitle = ' '.join(a.get('title',''))
         elif isinstance(a.get('title', ""), basestring):
@@ -46,4 +55,4 @@ def generate_model(lang, sites, mxParse=-1, mxSetSize=3):
 """
 Example
 """
-m = generate_model("English", ["bbc.com", "bbc.co.uk"], -1, 1)
+#m = generate_model("English", ["bbc.com", "bbc.co.uk"], -1, 1)

### 2015-12-10 paper/paper.tex
Some stylistic fixes to the paper as well as minor edits. Expanded image subsets to use the avg pixel comparator if used from the command line

@@
 \paragraph{}
-Generating datasetss for related problems
+Generating datasets for related problems.
 Another application is generating datasets for other related problems such as trying to 
@@
 Related Work
--- Computer Vision
+-- Computer Vision, Natural Language Processing
 
@@
 \section{Generating Salient Keyword/Phrase Sets}
+
+\paragraph{}
 Generating salient sets is fairly easy compared with establishing a language model. To get a set of 
@@
 \paragraph{}
-In this paper we choose a the combination:
+In this project we choose a the combination:
 $$1-frequencyInArticle(Word)/numberOfWordsInArticle$$
@@
 \section{Generating Image Sets}
+
+\paragraph{}
 In our project we require a large number of images with similar annotations of keywords for each language 
@@
 subset of images within these sets must be found. This can be done by finding the intersection of all the 
-sets. In our implemnetation, we first created subset that was the intersection of two sets and then 
+sets. In our implementation, we first created subset that was the intersection of two sets and then 
 iteratively performed the intersection of this subset with each other set of images. Since the number of 
@@
 \section{Generating Illustrations}
+\paragraph{}
 The last and final step in our project is how we visualize the image-sets and the keyword salience. Ideally we 
@@
 \section{Conclusion and Problems}
+\paragraph{}
 One problem we encountered was that the Google image seach API only allows for 100 searches per day for free, so 
@@
 \subsection{Language Model}
+\paragraph{}
 A possible extension of how we generate a language model is to take into account the time each article is written and 
@@
 In many languages their is a tendency for certain word-parts to take a certain order which may vary for a number of 
-reasons such as whether a phrase is a question or statement. In later iterations of our language model we can take 
+reasons such as whether a phrase is a question or statement. In later iterations of our language model, we would take 
 this into account and try to determine whether a language has such an order and when or whether it changes during 
@@
 It may be possible to determine whether a particular word is a noun, verb, etc. \ by considering their frequency 
-along-side closely occuring words and their order. But, this is a difficult task on its own.
+along-side closely occuring words and their order. However, this is a difficult task on its own.
 \paragraph{}
@@
 \subsection{Image Analysis and Partitioning of Image Sets}
+\paragraph{}
 A possible extension of this stage would be to incorporate machine learning and computer vision to be able to find 
-features and feature-groups within an image. Using features and feature-groups we may be able to find which features 
+features and feature-groups within an image. By using features and feature-groups, we may be able to find which features 
 or feature-groups relate to each keyword or keyword-set and pick images based on this. This step is already improved 
@@
 \subsection{Illustration}
+\paragraph{}
 The step of creating the illustration can be modified in a number of ways. The best method likely varies based on what 

### 2015-12-10 image_subsets/image_subsets.py

@@ -1,18 +1,28 @@
 #!/bin/python
 # -*- coding: utf-8 -*-
 
-import image_iterator
 import comparators.pixel_comparator
+import comparators.chained_image_comparator
+import comparators.avg_pixel_comparator
+import image_iterator
 import sys
 
 # Not really sets, since they may contain "duplicate" images(ie ones that when compared return True)
-def get_common_subset_of_image_sets(image_subsets, comparator):
+'''
+Input:
+    image_sets: A list of sets where each set contains a list of file paths for the images to be compared
+    comparator: A comparator that will be used to compare the images
+Output:
+    The common subset of all the image_sets
+'''
+def get_common_subset_of_image_sets(image_sets, comparator):
     if len(image_subsets) == 0:
         return None
         
-    current_image_set = image_subsets[0]
-    for image_set in image_subsets[1:]:
-        current_image_set = intersection_of_sets(current_image_set, image_set, comparator)
+    current_image_subset = image_sets[0]
+    for image_set in image_sets[1:]:
+        # Refine the subset
+        current_image_subset = intersection_of_sets(current_image_subset, image_set, comparator)
     
     return current_image_set
 
@@ -44,16 +54,7 @@ def parse_subsets(subset_file):
             curr_subset.append(curr_line.strip())
         
         curr_line = subset_file.readline()
-    '''for subset_line in subset_file:
-        print subset_line
-        curr_line = subset_line.strip()
-        if curr_line == '' and len(curr_subset) > 0:
-            subsets.append(curr_subset)
-            curr_subset = []
-            break
-            
-        curr_subset.append(curr_line)
-    '''
+
     if len(curr_subset) > 0:
         subsets.append(curr_subset)
     return subsets
@@ -93,7 +94,9 @@ if __name__=="__main__":
             
             print image_subsets
             if image_subsets:
-                print get_common_subset_of_image_sets(image_subsets, comparators.pixel_comparator.PixelComparator())
+                chained_comparators = [comparators.pixel_comparator.PixelComparator(), comparators.avg_pixel_comparator.AvgPixelComparator()]
+                comparator = comparators.chained_image_comparator.ChainedImageComparator(image_comparators=chained_comparators)
+                print get_common_subset_of_image_sets(image_subsets, comparator)
         except Exception as e:
             print e
             usage()

### 2015-12-10 image_subsets/comparators/avg_pixel_comparator.py
Removed print statements from avg_pixel_comparator and changed it to only support images whose pixels are returned as a (R, G, B) tuple

@@ -8,7 +8,7 @@ from PIL import Image
 
 class AvgPixelsComparator(object):
     # Want to be able to tighten or loosen the comparison constraints 
-    def __init__(self, num_kernels_horizontal=2, num_kernels_vertical=2, avg_comparator=lambda x, y: x == y):
+    def __init__(self, num_kernels_horizontal=2, num_kernels_vertical=2, avg_comparator=lambda x, y: x[0] == y[0] and x[1] == y[1] and x[2] == y[2]):
         # This is an approximate number of kernels
         self.__num_kernels_horizontal = num_kernels_horizontal
         self.__num_kernels_vertical = num_kernels_vertical
@@ -44,7 +44,6 @@ class AvgPixelsComparator(object):
                 
                 image1_y += image1_kernel_vertical_move_amt
                 image2_y += image2_kernel_vertical_move_amt
-                print kernel_avg_image1, kernel_avg_image2
                 if not self.__avg_comparator(kernel_avg_image1, kernel_avg_image2):
                     same_image = False
                     break
@@ -63,13 +62,13 @@ class AvgPixelsComparator(object):
         return float(image_dimension)/num_kernels_on_dimension
         
     def __get_colour_avg_of_kernel(self, kernel_x, kernel_y, kernel_width, kernel_height, image):
-        pixel_sum = 0
-        print "New Kernel"
+        pixel_sum = [0, 0, 0]
         for i in range(kernel_width):
             for j in range(kernel_height):
-                print kernel_x, kernel_y, i, j, image.getpixel((int(kernel_x) + i, int(kernel_y) + j))
-                pixel_sum += image.getpixel((int(kernel_x) + i, int(kernel_y) + j))
-        return pixel_sum / float(kernel_width * kernel_height)
+                pixel_colour = image.getpixel((int(kernel_x) + i, int(kernel_y) + j))
+                for k in range(3):
+                    pixel_sum[k] += pixel_colour[k]
+        return [pixel_sum[i] / float(kernel_width * kernel_height) for i in range(len(pixel_sum))]
             
     
 def usage():
